Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-09-10 Docs/Paper/LaTex/template.tex
Change of title
review 5.3 Experimental Results

\begin{document}
\title{Applying Multi-Core Model Checking and Maximum Satisfiability to Hardware-Software Partitioning}
\author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Helder Silva \and Lucas Cordeiro}

@@

ESBMC implement four approaches: ESBMC, ESBMC-SS, ESBMC-PS, ESBMC-PB, and ESBMC-$\nu$Z.

\begin{itemize}
\item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
\item{\textbf{ESBMC-SS:} This uses a sequential strategy \{1 ,2 ,\:...\:, Hmax\}, where there is no parallel controller, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC-SS; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
\item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}
\end{itemize}

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, $\nu$Z solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; $\nu$Z is typically faster than ILP by approximately $3$ times ({\it e.g.}, Patricia benchmark); however, $\nu$Z returns two TOs (time-outs) in Fuzzy and Mars benchmarks.

In contrast to $\nu$Z, ILP solves $6$ out of $7$ benchmarks. When ILP produces a result, it always provides the optimal solution. On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by $\nu$Z. On the other hand, ILP is faster than ESBMC in all benchmarks, except for the clustering.

Note that all ESBMC parallel versions produce better results than the sequential one. In particular, the ESBMC-PB implementation outperforms all other ESBMC approaches; the ESBMC-PB performance improves as the number of nodes and edges increase. One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$.$13$ times faster than ILP and $1$.$89$ times slower than $\nu$Z.

The ESBMC-PB implementation described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search} shows a significant performance improvement; when the amount of nodes is around $30$, ESBMC-PB does not outperform the optimization techniques employed by $\nu$Z and ILP tools. However, when the amount of nodes is approximately $150$, ESBMC-PB becomes three times faster than ILP, which is the most robust technique. When $\nu$Z explores a small amount of nodes, it is typically $30$ times faster ({\it e.g.}, CRC$32$) than ESBMC-PB and for intermediate nodes (around $150$ nodes), this performance improvement decreases to $1$.$9$ ({\it e.g.}, Clustering). When analyzing all benchmarks: RC$6$, Fuzzy, and Mars, ESBMC-PB produces TO or MO; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.

@@

Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using $\nu$Z, Matlab (ILP and GA), and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC\hyp{}PB) tools.

RC$6$ produced time out for all versions of ESBMC, $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except one. Fuzzy produced time-outs and memory-outs in all tools. ILP was the only one to solve Mars, while GA solved incorrectly all benchmarks.

Clustering described in Table~\ref{Experimental-results-of-the-complex-benchmarks} seems to be the limit to test the described tools, note that more than $150$ nodes lead to TO and MO. ILP shows robustness and produces results even for a high amount of nodes and edges.

@@

%ILP
\multirow{2}{*}{\textbf{ILP}}  
&  T(s)   &  2   &  1   &  2   &  649   &  1806    &  TO   &  5.42  \\
&  Hp   &  15   &  47   &  31   &  241   &  692    &  -   &  876  \\
\hline

>>>>

\begin{document}
\title{Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning}
\author{Alessandro Trindade\and Hussama Ismail\and Renato Degelo\and Edilson Galv\~ao\and Helder Silva \and Lucas Cordeiro}

@@

Table~\ref{Experimental-results-of-the-complex-benchmarks} shows the experimental results using Matlab (ILP and GA) and ESBMC (ESBMC\hyp{}MC, ESBMC\hyp{}PS, ESBMC\hyp{}PB, ESBMC\hyp{}$\nu$Z) tools.

There is no single tool for efficiently solving all HW-SW partitioning benchmarks. In particular, the best (proposed) solution is ESBMC-$\nu$Z, which solves $4$ out of $7$ benchmarks, but it does not find the optimal solution for the RC$6$ benchmark; however, ESBMC-$\nu$Z is faster than ILP in all supported benchmarks ({\it i.e.}, CRC$32$, Patricia, Dijkstra, Clustering), but it returns two TOs (time-outs) related to Fuzzy and Mars benchmarks.

In contrast to ESBMC-$\nu$Z, ILP solves $6$ out of $7$ benchmarks. When ILP produces a result, it typically provides the optimal solution. On the one hand, ILP execution time is slower than $\nu$Z in all benchmarks, which are supported by $\nu$Z. On the other hand, ILP is faster than ESBMC-SS, ESBMC-PS, and ESBMC-PB in all benchmarks, except for the clustering.

Note further that all multi-core ESBMC implementations produce better results than the sequential one. In particular, ESBMC-PB implementation outperforms all other multi-core ESBMC approaches, where its performance improves as the number of nodes and edges increase. One notable case is the clustering benchmark, when verified by ESBMC-PB, it executes $3$ times faster than ILP and $1$.$89$ times slower than ESBMC-$\nu$Z. However, when the amount of nodes is around $30$, ESBMC-PB does not outperform ESBMC-$\nu$Z and ILP tools. When analyzing all benchmarks, ESBMC-PB produces TO or MO for RC$6$, Fuzzy, and Mars; however, the results are still promising if we take into consideration that $\nu$Z and Matlab are state-of-the-art tools with respect to optimization problems.

%When ESBMC-$\nu$Z explores a small amount of nodes, it is typically $30$ times faster ({\it e.g.}, CRC$32$) than ESBMC-PB and for intermediate nodes (around $150$ nodes), this performance improvement decreases to $1$.$8$ ({\it e.g.}, Clustering).

@@

Note that RC$6$ produced time out for all implementations of ESBMC; $\nu$Z e GA did not produce the correct answer, and ILP solves correctly all benchmarks, except for Fuzzy, which produced time-outs and memory-outs in all tools that aim to find the exact solution. ILP was the only one to solve Mars, while GA solved all benchmarks incorrectly.

The clustering benchmark seems to be the limit to test the ESBMC (described) implementations; note, however, that more than $150$ nodes lead to TO and MO. ILP shows robustness and produces results even for a high number of nodes and edges.

@@

\bottomrule[1.5pt]
%ILP
\multirow{2}{*}{\textbf{ILP}}  
&  T(s)   &  2   &  1   &  2   &  649   &  1806    &  TO   &  5.42  \\
&  Hp   &  15   &  47   &  31   &  241   &  692    &  -   &  876  \\
\hline
